A Case Study in Preserving a High Energy Physics Application

### 2014-03-14 paper.tex
modify the evaluation part

The configuration of earth machine. The configuration of our virtual machine. The configuration of amazon ec2.
each vm: data download time; untar time; script execution time;

\subsection{Evaluation of Solution 2}
The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About 40\%  of the total execution time is consumed to prepare relevant software environment. The cvs command is called to check out 23 packages from CMSSW and three git repositories are cloned.

@@

This solution does not support mining of implicit dependencies.

\subsection{Evaluation of Solution 4}

@@

The data size of Solution 4 is shown in Table~\ref{table:datasize-3rd}. The
data categories are more complex than our imagination. Except the data stored in
Hadoop and the necessary set of software, files from local filesystem and several remote filesystems, such as PanFS, CVMFS, NFS, and AFS, are also necessary for the reproduction of the program.

\subsection{ Data size Comparison of Solution 2 and 4}

\subsection{Execution Time Comparison of Solution 2 and 4}

@@

>>>>

\subsection{Execution Time Comparison of Solution 2 and 4 on the Original Machine}

The breakdown of execution time of Solution 2 is shown in Table~\ref{table:time-2nd}. About 40\%  of the total execution time is consumed to prepare relevant software environment. The cvs command is called to check out 23 packages from CMSSW and three git repositories are cloned.

@@

@@

@@

\subsection{Data Size Comparison of Solution 2 and 4 on the Original Machine}

Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
The third column is corresponding to the data size of Solution 4. 
Solution 2 does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. Howerver, it is hard to figure out the named size of each local source.
